Collaborative Visual Analysis on the Web with RCloud

### 2015-06-25 casestudies.tex
yes

\section{Case Study\label{sec:casestudy}: visual exploration of topic modeling in RCloud}

@@

LDAVis combines text analysis, dimensionality reduction and
interactive visualization. Text analysis is performed by
combining a standard R library to fit LDA models using
Gibbs sampling~\cite{} with custom R code written by the
developers. The analysis module is a single R function
exposed to the web application via the Javascript-R RPC
mechanism described in Section~\ref{sec:system};
thus analysis is performed remotely on an RCloud server.

>>>>

\section{Case Study\label{sec:casestudy}: visual exploration of topic modeling}

@@

LDAVis combines text analysis, dimensionality reduction and
interactive visualization. Text analysis is performed by
combining a standard R library to fit LDA models using
Gibbs sampling with custom developed R code.
The analysis module is a single R function
exposed to the web application via the Javascript-R RPC
mechanism described in Section~\ref{sec:system};
thus analysis is performed remotely on an RCloud server.
